Plots_Genome

### 2025-07-14 Code/Plots_Genome.Rmd
line 177 `Km_mM_min = min(Km_mM, na.rm = TRUE)`

>>>>

```{r, ProchlorococcusEnzymeKmsTrim, fig.cap = ProchlorococcusEnzymeKmsTrim_cap, fig.width = 20, fig.height = 10}

ProchlorococcusEnzymeKmsTrim_cap <- glue("**Comparison of log~10~(K~m~ for O~2~ in mM) vs.genes encoding O~2~ utilizing enzymes in *Prochlorococcus***, faceted by their respective strains.",
                                     "Symbol color corresponds to number of genes encoding O~2~ utilizing enzymes.",
                                     "Symbol shape corresponds to whether the K~m~ was measured in the respective enzyme, or inferred from the K~m~ of a similar enzyme.",
                                     "Black vertical line corresponds to the range of K~m~ for O~2~.",
                                     "Vertical translucent bars correspond to concentrations of O~2~ in which *Prochlorococcus* strains were grown.",
                                     "K~m~ values were obtained from other organisms, excluding Ribulose bisphosphate carboxylase.",
                                     "Symbol absence means no sequences were detected in the genome."
                                     )

(ProchlorococcusEnzymeKmsTrim <- MergedData %>%
         Taxa == "Prokaryote",
         EnzymeName %in% c("decaprenylphospho-beta-D-ribofuranose 2-dehydrogenase", "ubiquinol oxidase (non-electrogenic)","acireductone dioxygenase (Ni2+-requiring)", "pyridoxal 5'-phosphate synthase", "(S)-2-hydroxy-acid oxidase", "bacterial non-heme ferritin")) %>% 
  mutate(#Km_mM_min = min(Km_mM, na.rm = TRUE), 
  # mutate(Km_mM = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
  #                          TRUE ~ Km_mM),
  #        Km_mM_min = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
  #                          TRUE ~ Km_mM_min),
  #        Km_mM_max = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
  #                          TRUE ~ Km_mM_max)) %>% 
        legend.text = element_text(size = 30))
  )   #change legend text font size
